### 2021-04-17 paper/conclusion.tex
Move to Holger's templates and some other - cannot remember - fixes.
Enforced 88 character limit.
Updates and notes for more updates for the introduction.
Bring paper up to date for CRC Discussion Series. (#2)
Co-authored-by: Tobias Raabe <raabe@posteo.de>

We propose a simulation based model of infectious disease transmission that is designed to predict the effects of fine-grained social distancing policies. In particular, the model can be used to model policies such as several ways of splitting school classes or work reduction policies that affect essential and non-essential workers differently. Both policies would be hard to implement in standard SEIR or agent based simulation models.

@@

Despite these encouraging results we still see the model as work in progress and plan to implement more features such as a detailed model of testing and contact tracing. Moreover, the estimation of the infection probabilities and the model fit will improve as more data becomes available.

>>>>

We propose a simulation based model of infectious disease transmission that is designed
to predict the effects of fine-grained social distancing policies. In particular, the
model can be used to model policies such as several ways of splitting school classes or
work reduction policies that affect essential and non-essential workers differentially.
Both policies would be hard to implement in standard SEIR or agent based simulation
models.

@@

Despite these encouraging results we still see the model as work in progress.
We plan to implement more features, in particular allowing age and symptoms to affect
the probability to seek and receive a test, opening the way to show the effect of
different testing policies, such as those proposed by \cite{Troeger2020}.
Moreover, the estimation of the infection probabilities and the model fit will improve
as more data becomes available.

### 2021-04-17 paper/introduction.tex
Bring paper up to date for CRC Discussion Series. (#2)
Co-authored-by: Tobias Raabe <raabe@posteo.de>

    \item Policies can be implemented as shutting down contact types entirely or
          partially. The reduction of contacts can be random or systematic. For example,
          it is possible to implement A/B schooling where only one half of each class
          attends and the attending half switches on a weekly bases.

>>>>

    \item Policies can be implemented as shutting down contact types entirely or
          partially. The reduction of contacts can be random or systematic. For example,
          it is possible to implement split class schooling where only one half of each
          class attends and the attending half switches on a weekly bases.

### 2021-04-17 paper/literature_review.tex
Bring paper up to date for CRC Discussion Series. (#2)
Co-authored-by: Tobias Raabe <raabe@posteo.de>

The above assessment of epidemiological models is not meant as a critique. We are aware
that those models were not designed to predict the effect of fine-grained social
distancing policies in real time and are very well suited to their purpose. We invite
epidemiologists to provide feedback and collaborate to improve our model.

>>>>

The above assessment of epidemiological models is not meant as a critique. We are aware
that these models were not designed to predict the effect of fine-grained social
distancing policies in real time and are very well suited to their purpose. We invite
epidemiologists to provide feedback and collaborate to improve our model.

### 2021-04-17 paper/model/course_of_disease.tex
Bring paper up to date for CRC Discussion Series. (#2)
Co-authored-by: Tobias Raabe <raabe@posteo.de>

First, infected individuals will become infectious after one to five days. About one
third of people stays asymptomatic. The rest develops symptoms about one to two days
after they become infectious. Modeling asymptomatic and pre-symptomatic cases is
important because those people do not reduce their contacts or demand a test and can
potentially infect many other people \citep{Donsimoni2020}.

@@

It would be easy to make the course of disease even more fine-grained. For example, we
could model people who require hospitalization but not intensive care. So far we opted
against that because only the ICU capacity might become a bottleneck in Germany.

>>>>

First, infected individuals will become infectious after one to five days. About one
third of people remain asymptomatic. The rest develop symptoms about one to two days
after they become infectious. Modeling asymptomatic and pre-symptomatic cases is
important because those people do not reduce their contacts or demand a test and can
potentially infect many other people \citep{Donsimoni2020}.

@@

It would be easy to make the course of disease even more fine-grained. For example, we
could model people who require hospitalization but not intensive care. So far we opted
against that because only the intensive care capacities are feared to become a
bottleneck in Germany.

### 2021-04-17 paper/model/policies.tex
Bring paper up to date for CRC Discussion Series. (#2)
Co-authored-by: Tobias Raabe <raabe@posteo.de>

Some policies can be easily implemented if the background characteristics are suitably
extended. For example, a schooling policy with A/B schooling, where each half attends
school every other week can be implemented by storing whether the child would attend in
even or odd weeks in the background characteristics and then using that information in
the policy function.

>>>>

Some policies can be easily implemented if the background characteristics are suitably
extended. For example, a schooling policy of splitting and rotating classes,
where each half attends school every other week can be implemented by storing
whether the child would attend in even or odd weeks in the background characteristics
and then using that information in the policy function.

### 2021-04-17 paper/model/testing.tex
Bring paper up to date for CRC Discussion Series. (#2)
Co-authored-by: Tobias Raabe <raabe@posteo.de>

In our empirical estimation we use a very simplified testing model where the number
of tests to be distributed is calculated from estimates for the ratio of known to all
infections.\footnotemark
\footnotetext{The Dunkelzifferradar project publishes daily estimates of the dark figure
of infections under \url{https://covid19.dunkelzifferradar.de/}}
Using these estimates as well as data on the test distribution
over age groups by the RKI\footnotemark
\footnotetext{https://ars.rki.de/Content/COVID19/Main.aspx}
we allocate tests firstly among the symptomatic
and then randomly allocate tests to newly infected to fit the German test distribution.

>>>>

In our empirical estimation we use a very simplified testing model where the number of
tests to be distributed is calculated from estimates for the ratio of known to all
infections.\footnote{The Dunkelzifferradar project publishes daily estimates of the dark
figure of infections under \url{https://covid19.dunkelzifferradar.de/}} Using these
estimates as well as data on the test distribution over age groups by the
RKI\footnote{https://ars.rki.de/Content/COVID19/Main.aspx} we allocate tests firstly
among the symptomatic and then randomly allocate tests to newly infected to fit the
German test distribution.
